---
title: "Assignment1"
author: "JasonChen s4657923"
date: "11/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
summary(cars)
```

# Part 1
# RMarkdown Editing

### 3 
R Markdown is an authoring format that enables easy creation of dynamic documents, presentations, and reports from R.

### 4
***In the above use bold and italics for editing.***

### 5
[link] (https://rmarkdown.rstudio.com/lesson-8.html)

### 6
```{r fastfood}
library(tidyverse)
fastfood<- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')
```

### 7
```{r}
fastfood %>% head(10)
library(knitr)
kable(fastfood[1:10,1:5])

```

library(janitor)

### 8
```{r}
fastfood %>%
  filter(calories>1000)
```

### 9
```{r}
dont_eat_this<-fastfood %>%
  filter(total_fat>40 & total_carb>80)
```

### 10
```{r}
fastfood%>%
  filter(restaurant=='Mcdonalds')
```

# Part 2
### 11
```{r}

library(skimr)
library(tidyverse)
fastfood<- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')
skim(fastfood)
```

### 12
```{r}
fastfood%>%
  count(restaurant)
```

### 13
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(mean_calories=mean(calories))
```

### 14
```{r}
fastfood%>%
  mutate(average_calories=mean(calories))
  
```

### 15
```{r}
library(ggplot2)
ggplot(fastfood,
  aes(restaurant,total_fat)) +
  geom_point()

```
In conclusion, the total fat provided per restaurant is indistinguishable in general, but Burger King and Mcdonald's are the only two restaurants that offer higher-than-100-fat products. Where some of the restaurants like Subway, Diary Queen and Chick Fil-A offer o fat products.

### 16
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(max_total_fat=max(total_fat))
fastfood%>%  
  mutate(max_total_fat=max(total_fat))
```

### 17
```{r}
ggplot(fastfood,
  aes(sugar,protein)) +
  geom_point()
```

# Part 3
### 18
```{r}
fastfood%>%
  mutate_if(is.character,factor)
```

library(tidyverse)

### 19
```{r}
fastfood%>%
  mutate(calories_type = cut_number(calories, n=3, labels = c("low", "med", "high")))
  calories_type<-fastfood%>%mutate(calories_type = cut_number(calories, n=3, labels = c("low", "med", "high")))
```

### 20
```{r}
ggplot(calories_type, 
  aes(calories,calories_type,)) +
  geom_col() +
  theme_light()+
  labs(x="Restaurantst", y="Calories Types",  
       title="Data Visualisation", caption="Image : Calories type")+
  facet_wrap(~restaurant)


```


### 21
```{r}
trans_fat_percentage<-calories_type %>%
  group_by(restaurant) %>%
  mutate(trans_fat_percentage = trans_fat/total_fat * 10)
```

### 22
```{r}
ggplot(trans_fat_percentage, 
  aes(total_fat,trans_fat_percentage,)) +
  geom_col() +
  theme_light()+
  labs(x="Restaurant", y="Trans Fat Percentage",  
       title="Data Visualisation", caption="Image : Trans Fat percentage")+
  facet_wrap(~restaurant)
```

### 23
```{r}
trans_fat_percentage%>%
  group_by(restaurant)%>%
  summarise(mean_total_fat=mean(total_fat))
```

### 24
```{r}
trans_fat_percentage %>%
  group_by(restaurant) %>%
  summarise(average_total_fat = mean(total_fat)) %>%
  ungroup() %>%
  mutate(restaurant = fct_reorder(restaurant, average_total_fat)) %>%
  ggplot(aes(restaurant, average_total_fat)) +
  geom_col() +
  coord_flip() +
  labs(x="Names of restaurant", y="Average Total Fat", title="Data Visualisation", caption="Image : Bar Graph")+
  theme_light()
```







